On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
ye
Rehn shout out

Our guarantees also hold for a related (and perhaps more commonly posed) optimization problem that seeks a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}). Importantly, we never make assumptions on learned dictionaries (e.g., that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing for $m = N$ waveforms). %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.

>>>>

Our guarantees also hold for a related (and perhaps more commonly posed, e.g. \cite{rehnsommer2007}) optimization problem seeking a dictionary minimizing the average number of elementary waveforms required to reconstruct each sample of the dataset (Thm.~\ref{SLCopt}). Importantly, we never make assumptions on learned dictionaries (e.g., that they, too, be injective over some domain) beyond an upper bound on dictionary size, which is necessary to avoid trivial solutions (e.g., allowing $m = N$). %That is, every pair of solutions of comparable size has some number of dictionary elements in common (up to noise), and similarly so for the coefficients of sparse codes they induce.
